SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/bio_MTedit.tex
table 1 fixed
k connected fix

If a VTS is $k$-connected, every pair of compartments remain reachable
after dropping $k-1$ vesicles.
%
This property of VTSs have been considered informative and
studied~\cite{shukla}.
%
Here we have build an \emf{efficient} tool that studies properties of
VTSs that are not $k$-connected, from some $k$.

>>>>

A VTS is {\em $k$-connected} if every pair of compartments remain
reachable after dropping $k-1$ vesicles.
%
This property of VTSs have been considered informative and
studied by~\cite{shukla}.
%
Here we have build an {\em efficient} tool that studies properties of
VTSs that are not $k$-connected, from some $k$.
